---
title: "BKA_Kriminalstatistik_2019_data_analysis"
author: "Peter von Bodelschwingh, Joshua Gawenda"
date: "12 12 2020"
output:
  html_document:
    df_print: paged
  pdf: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(sjmisc)
library(tidyverse)
library(readxl)
library(GDINA)
#install.packages("geojsonio")
#install.packages("mapproj")
#install.packages("scales")
library(geojsonio)
library(broom)
#library(scales)
```

# German crime statistics 2019 - A data analysis

## Introduction

In this data analysis we are going to take a look at the German crime statistics from the year 2019, the special version we are looking at also
shows the crime distribution about different sized cities. The data is divided for all 16 German provinces and into a general section for the whole
country. <br/>
There are also multiple files that help to determine what can be deducted from a data analysis of this set and what is out of scope. <br/>
The data set is taken from the  "Bundeskriminalamt" - the leading institution of crime detection in Germany. <br/>
The original data set can be found here: 
[BKA Dataset](https://www.bka.de/DE/AktuelleInformationen/StatistikenLagebilder/PolizeilicheKriminalstatistik/PKS2019/PKSTabellen/LandFalltabellen/landFalltabellen.html) <br/>
This data set only shows absolute numbers for all provinces in Germany, so to make the statistics comparable over all the different provinces we
also included another data set, that shows the number of inhabitants for every province and the whole country. <br/>
This data set can be found here: 
[German Inhabitants](https://www.destatis.de/DE/Themen/Laender-Regionen/Regionales/Gemeindeverzeichnis/Administrativ/02-bundeslaender.html) <br/>
Later you will see that we imported on more data set. This one is generated out of a PDF from the documentation for the first data set and therefore
is not available in the format we have online. It holds information about the so called sum keys of the main data set and is later used to decouple
the main data set.

### Sum Keys

To understand a big part of the analysis you have to understand what sum keys are, this is what we are going to describe in this chapter. <br/>
A key in the data set we use represents one type of crime, every crime has its own distinct key. Some crimes are just a composite of multiple other
crimes, their key is then called a sum key, so every crime that is not a sum, has no children but only a parent crime. <br/> 
A key is made out of six digits, where every digit is read as a single one from left to right. In general every key that starts with the same digits 
is part of the same sum key, the sum key is then identified with the same starting digits followed by zeros. However this is not true in every case, 
some keys that end with zero have no children and therefore are no sum keys, the sum key for those keys is in most cases represented by a "*"-sign. <br/>
One general section of crimes is therefore represented by only the first digit. There are also two whole sections of keys that are only made out of
sum keys and are used by the police to study different fields of crimes.

## Import

The first step to every data analysis is to import the data into your project. The data we chose is available as an excel file so we use the 
package "readxl" to import the sets from excel. For the import to work properly we had to remove some unnecessary header lines in the main data
set, we did that by specifying a "range" in the read_excel command. <br/>
The "SumKeys" data set was created by us, therefore every optimization for importing where made while creating the set. <br/> 
Finally we also import the data set for the inhabitants, since this data set is not part of the main analysis, we decided to also edit it in
excel to optimize it for the import and remove data that we do not need for the analysis.
 
```{R Import}
originalSet <- read_excel("DataSets/PKS_crime_statistics.xlsx", sheet = "Data",range = "A8:U18777") 
sumKeysImport <- read_excel("DataSets/PKS_crime_statistics.xlsx", sheet = "Sumkeys")
germanInhabitants <- read_excel("DataSets/02-bundeslaender.xlsx", sheet = "inhabitants")
```

### Renaming

After the import, the names of the original data set got lost and are not descriptive anymore. To assure that the usage later on is more understandable
we renamed the data set.

```{r Renaming}
originalSet <- originalSet %>% 
                rename(
                  key = '1',
                  crime = '2',
                  province = '3',
                  detected_cases = '4',
                  detected_cases_percent = '5',
                  not_executed_cases = '6',
                  not_executed_cases_percent = '7',
                  distribution_under_20K = '8',
                  distribution_20K_to_100K = '9',
                  distribution_100K_to_500K = '10',
                  distribution_over_500K = '11',
                  distribution_unknown = '12',
                  gun_threatened = '13',
                  gun_shot = '14',
                  solved_cases = '15',
                  solved_cases_percent = '16',
                  suspects = '17',
                  male = '18',
                  female = '19',
                  non_german ='20',
                  non_german_percent = '21'
                  )
```
 
As a last step of importing, we can merge the inhabitants data frame into the original data frame for the analysis. This would allow to use the
number of inhabitants easily in any calculation from here on.

```{r Merge_Inhabitants}
originalSet <- merge(originalSet, germanInhabitants, by = "province") %>% arrange(key)
head(originalSet)
```

## Tidy

This next step includes checking for missing values and in our case splitting the data frames up, so that the provinces are decoupled from the values
for whole Germany. We also need to remove all sum keys from the actual capture keys.

### Check non NA

If the data set contains empty values they are marked as NA and have to be handled somehow. However, this data set has no such values as shown in the
next code chunk. Here we filter for NA values in any column and check if the row count is 0 in the end.

```{r NA_Check}
nrow(filter_at(originalSet, 1:21, any_vars(is.na(.)))) == 0
```

### Decouple

Like describe in the "Sum Key" section, the original data set is a mix of sum keys and capture keys. In order to not count twice in some operations
we remove the sum keys from the capture keys, so the main analysis can focus on the capture keys. <br/>
The sum keys set that we imported has two columns, one for the key and one with the value "Y" for every capture key and a "N" for every sum key. The 
two key sections that are only made out of sum keys are not reported in the set, so can be handled as "NA".

```{r Filtering_Keys}
captureKeys <- sumKeysImport %>% filter(grepl("Y",is_sum_key))
sumKeys <- sumKeysImport %>% filter(!grepl("Y",is_sum_key))
```

To check, that the keys after the filter are all correct, we created a small algorithm that checks for sum keys based on the the rules described in
the "Sum Keys" chapter. The code takes a while to run, that is why we saved the result in a vector. 

```{r Manual Sum_Key_Check}
#filteredKeys <- c()
#for (key1 in captureKeys$key) {
#  if (!key1 %in% filteredKeys) {
#    for (key2 in captureKeys$key) {
#      if (!key2 %in% filteredKeys) {
#        if (key1 != key2) {
#          if (regexpr(paste("^", str_remove(key2, "0+$"), sep = ""), key1)[1] == 1) {
#            filteredKeys <- append(filteredKeys, key2)
#          }
#        }
#      }
#    }
#  }
#}
filteredKeys <- c("133000","141100","231200","305000","310000","315000","325000","326000","335000","340000","345000","350000","390000","435000","436000","620010","655010","670010","670020","670030")
```

After checking the resulting keys manually we found, that the keys "141100", "231200" and "133000" were marked as capture keys, but are sum keys,
so these keys have to be removed from the capture keys and added to the sum keys.

```{r Correct_Key_Filter}
captureKeys <- sumKeysImport %>% filter(grepl("Y",is_sum_key) & !(key %in% c("141100","231200","133000")))
sumKeys <- sumKeysImport %>% filter(!grepl("Y",is_sum_key) | (key %in% c("141100","231200","133000")))
```

### Filter final data frames

First to reduce duplicate data, we filtered out all crime descriptions into its own data frame, to it can be looked up afterwards.

```{r Category}
crimeCategories <-
  originalSet %>% filter(grepl("[0-9]0{5}", key)) %>%
  select(key, crime) %>%
  unique() %>%
  mutate(key = str_replace_all(key, "00000", ""))

originalSet <- originalSet %>% 
  mutate(category = substring(key, 1,1)) %>% 
  select(category, !category) %>% 
  mutate(category = ifelse(category%in%crimeCategories$key,crimeCategories[as.integer(category)+1,2],"Other"))
```


```{r Crime_Frame}
crimeOverview <- originalSet %>% select(key, crime) %>% unique()
crimeOverview <- arrange(crimeOverview, key)
head(crimeOverview)

originalSet <- originalSet %>% select(!crime)
```
    
## Transform

In the final step before visualizing the data we need to check all the types of the values in each column an change them to a type that is usable
for our analysis. We can also remove and create new Columns if necessary. In the end we are also splitting the original data frame up based on the
provinces and the sum keys determined before.

### Transforming data types

In this step we first check for the different data types we have in every column. We expect to have characters as the key, a factor for the provinces
and every other column should be a number.

```{r Type_Check}
sapply(originalSet, class)
```
Except for the province all values have the type expected, the next step is to transform the province into a factor.

```{r Factorize_Province}
originalSet$province <- as.factor(originalSet$province) 
originalSet$category <- as.factor(originalSet$category)

sapply(originalSet, class)
```

```{r}
c1 <- levels(originalSet$category)[1]
c2 <- levels(originalSet$category)[2]
c3 <- levels(originalSet$category)[3]
c4 <- levels(originalSet$category)[4]
c5 <- levels(originalSet$category)[5]
c6 <- levels(originalSet$category)[6]
c7 <- levels(originalSet$category)[7]
c8 <- levels(originalSet$category)[8]
c9 <- levels(originalSet$category)[9]
```


### Remove calculated columns

Some columns in the data set are just calculated from the given data, so to remove the possibility of a calculation error, we remove these columns
and add them on our own, once they are needed in the analysis.

```{r Select_Useful_Columns}
originalSet <- originalSet %>% select(key, category, province, inhabitants, detected_cases, solved_cases, not_executed_cases, suspects, male, female, non_german, gun_threatened, gun_shot, distribution_under_20K, distribution_20K_to_100K, distribution_100K_to_500K, distribution_over_500K, distribution_unknown)
```
### Split up data

This could also be part of the tidy step, but to reduce the amount of duplicate code for all checks, we split the data at the end. Therefore, we
merge both key frames together with the original data set to separate the sum keys and the capture keys into separate data frames.

```{r Province_Id include=FALSE}
province_ids <- data.frame (province = c("Baden-Württemberg","Bayern","Berlin","Brandenburg","Bremen","Hamburg","Hessen","Mecklenburg-Vorpommern","Niedersachsen","Nordrhein-Westfalen","Rheinland-Pfalz","Saarland","Sachsen-Anhalt","Sachsen","Schleswig-Holstein","Thüringen", "Bundesrepublik Deutschland"),
                  province_id = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16", "17"))
originalSet <- originalSet %>% merge(province_ids, by = "province")
```

```{r NA_Check}
originalSet %>% filter_at(vars(1:19), any_vars(is.na(.)))
```


```{r Split_Original_In_Sum_Capture}
captureValues <- merge(originalSet, captureKeys) %>% select(!is_sum_key)
sumValues <- merge(originalSet, sumKeys) %>% select(!is_sum_key)
```

With the sum keys now separated, we also divide both data frames into the values for the provinces and the values for whole Germany.

```{r Separate_Province}
germanCaptureSet <-
  captureValues %>% filter(grepl("Bundesrepublik Deutschland", province))
provinceCaptureSet <-
  captureValues %>% filter(!grepl("Bundesrepublik Deutschland", province))

germanSumSet <-
  sumValues %>% filter(grepl("Bundesrepublik Deutschland", province))
provinceSumSet <-
  sumValues %>% filter(!grepl("Bundesrepublik Deutschland", province))
```

To check that the sum keys from before where separated correct we check that the sum of all detected cases in each German set is equal to the sum 
for the detected cases in the province set.

```{r Sum_Key_Check}
sum(germanCaptureSet$detected_cases) == sum(provinceCaptureSet$detected_cases)
sum(germanSumSet$detected_cases) == sum(provinceSumSet$detected_cases)
```

## Prepare Map

Before our analysis can start, we want to display some data on a map, with all German provinces. In this step we prepare the empty map, so that it can
easily be used later on.

```{r}
province_json <- geojson_read("provinces.json", what = "sp")
empty_map <- tidy(province_json, area = "code") %>% mutate(province_id = id)

ggplot(empty_map, aes(long, lat, group = group)) +
  geom_polygon(fill="white", color="grey") +
  theme_void() +
  coord_map()
```



```{r, echo=FALSE}
options(scipen=999)
```
    
## Analyse 

Once the data is imported, tidied and transformed the analysis can start. To first get a general impression over the data that we have, we
used the standard plot command, that creates a simple chart for every column. The data frame that we use for all of the next instructions
is the one with only the values for whole Germany. We first want to find correlations in there. <br/>
To make the first general data analysis more readable, we need to remove the outliers in the data. All the data in this data set is bound to the 
number of detected cases, so if the number of detected cases is 0 all other columns will also be 0 and the other way around, if there is a high
number of detected cases, the possibility of high numbers in the other columns is pretty high (Those cases will be analyzed later on). <br/>
To find the number of detected cases where there are the most cases, we find the mean of detected cases. To do that we use the summary
function of R.

```{r Find_Cases_Mean}
summary(germanCaptureSet$detected_cases)
```

Now we just filter out all rows where the number of detected cases is larger than 7172. For now we are also not interested in the rows where there
are no cases, so we also filter out those.

```{r Filter_For_Number}
cutSet <- filter(germanCaptureSet, detected_cases > 0 & detected_cases <= 7172)
summary(cutSet$detected_cases)
```

To now get a general view on how the data is structured across the data frame we use the plot command, that creates simple plots for every
column in the frame.

```{r}
plot(cutSet, main = "General Overview", col = "#000000", pch = 19)
```

Based on these plots we found a few interesting correlations of data that we now are going to discuss in detail.


############################
############################
Steps:
1. Detected vs Solved
2. Detected/Solved vs Suspects
3. Suspects vs Male/Female/Non_German
4. Distribution
5. Funny Rankings for the end (inhabitants from provinces) -> filter out the 6 top categories (first letter in key)
############################
############################

### Detected Cases vs Solved Cases

The first thing that we noticed was, that there seems to be a relation between the number of detected cases and the number of solved cases. 
Next we enlarge this plot and filter out all rows where the number of solved cases is larger than the number of detected cases, because those would 
be part of a measurement error. We again also remove those cases where the number of detected cases is 0.

```{r Filter_Impossible_Solvage_Rate}
filtered <- filter(germanCaptureSet, detected_cases >= solved_cases & detected_cases > 0)
```

```{r Solvage_Rate}
ggplot(filtered, aes(detected_cases, solved_cases, color = category)) +
  geom_point(show.legend = T) +
  geom_smooth(method = "lm", fullrange = T, show.legend = F) +
  geom_abline(coef = c(0, 1)) +
  labs(title = "Detected vs. Solved", y = "Solved Cases", x ="Detected Cases")
```

This plot shows the relation between detected and solved cases for each major crime category.
The black line displayed in this plot shows the optimal line, where the number of detected cases is equal to the number of solved cases, so those crimes
where every case was solved. The closer a dot or a colored line is to this line, the higher is the solvage rate for the specific crime. <br/>
Lets now take a closer look at the different solvage rates.

```{r Calc_Solvage_Rate}
filtered <- filtered %>% mutate(solvage_rate = solved_cases/detected_cases*100)
ggplot(filtered, aes(category, solvage_rate, fill = category)) +
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  labs(title = "Solvage Rate", x = "Rate in Percent")
```

Lets also get the number to these graphs.

```{r}
descr(filter(filtered, category == c2)$solvage_rate)
c2
descr(filter(filtered, category == c3)$solvage_rate)
c3
descr(filter(filtered, category == c4)$solvage_rate)
c4
descr(filter(filtered, category == c5)$solvage_rate)
c5
descr(filter(filtered, category == c6)$solvage_rate)
c6
descr(filter(filtered, category == c7)$solvage_rate)
c7
descr(filter(filtered, category == c8)$solvage_rate)
c8
descr(filter(filtered, category == c9)$solvage_rate)
c9
descr(filter(filtered, category == c4 | category == c5)$solvage_rate)
"Crimes associated with theft"
descr(filtered$solvage_rate)
"General"
```

As can be seen in these plots, there is a high variation in the solvage rate of cases based on their category. In general the solvage rate is very high,
the general median lies at 72% solvage. There are just two exceptions, which are those crimes associated with theft, these lie around 36% solvage rate.
There is also one more crime category that stands out, every crime associated with murder, this has an extremely low inner quartile range which means, 
that the solvage rate there is very consistent. <br/>
When looking back at the plot, there are together with the murder category two more categories, that have a high mean solvage rate and a low inner
quartile range. These categories are special cases in the data set, you can assume that there is a specific reason behind the relatively consistent and
high solvage rate, this could be for example, that those cases are treated with a higher importance than others or, that those cases are easier to solve
or a completely different reason. <br/> 
<br/>
Now that we analyzed the solvage rate for the different crime categories for whole Germany, we can take a quick look at the rates for the different 
provinces. To keep this part short, we just used the overall mean solvage rate for every province instead of separating it into to different categories.

```{r Solvage Rate}
province_filtered <- provinceCaptureSet %>%
  filter(detected_cases >= solved_cases & detected_cases > 0) %>%
  mutate(solvage_rate = solved_cases / detected_cases * 100) %>%
  select(province_id, solvage_rate)

province_filtered <- aggregate(province_filtered, list(province_filtered$province_id),FUN=mean) %>% 
  select(!province_id) %>% 
  rename(province_id = "Group.1")

map_data = empty_map %>% left_join(., province_filtered, by = "province_id")

ggplot(map_data, aes(long, lat, group = group, fill = solvage_rate)) +
  geom_polygon(color = "black") +
  geom_polygon(data = filter(map_data, province_id == 3), color = "black") +
  geom_polygon(data = filter(map_data, province_id == 5), color = "black") +
  theme_void() +
  coord_map() + 
  labs(title = "Province Mean Solvage Rate", fill = "Rate in percent")
```

When looking on this map, it is clearly visible, that there are five relatively dark provinces on the map, which means, that they have the lowest solvage
rate in Germany. The four out of these provinces are the smallest provinces in Germany while the fifth has no connection in size to the others. <br/>
To now get a better picture on which provinces are the most dangerous, based on their mean solvage rate and their crimes per inhabitant, we create a
second map that shows the crimes per 10.000 inhabitants.

```{r}
province_filtered <- provinceCaptureSet %>%
  filter(detected_cases >= solved_cases & detected_cases > 0) %>%
  mutate(crime_rate = detected_cases / inhabitants * 10000) %>%
  select(province_id, crime_rate) %>% 
  mutate(province_id = as.integer(province_id))

province_filtered <- aggregate(province_filtered, list(province_filtered$province_id),FUN=sum) %>% 
  select(!province_id) %>% 
  rename(province_id = "Group.1") %>% 
  mutate(province_id = as.character(province_id))

map_data = empty_map %>% left_join(., province_filtered, by = "province_id")

ggplot(map_data, aes(long, lat, group = group, fill = crime_rate)) +
  geom_polygon(color = "black") +
  geom_polygon(data = filter(map_data, province_id == 3), color = "black") +
  geom_polygon(data = filter(map_data, province_id == 5), color = "black") +
  theme_void() +
  coord_map() + 
  labs(title = "Province Mean Crimes", fill = "Crimes per 10.000 inhabitants")
```

And again, the three lightest spots on the map, therefore the ones with the highest crime rate, are the three smallest provinces in Germany. Also the 
other two provinces from the last map have a relatively light tint, a bit above the average, which could indicate a possible relationship between
the crime rate and the solvage rate. <br/>
It is also interesting to see, that the eastern provinces have a slightly higher crime rate than the rest of Germany, which could have a possible
explanation in the fact, that Germany was separated by a wall for many years. After the wall was destroyed, the western provinces implemented a new tax
to support the eastern provinces, because they needed financial help after those years. So a because the eastern provinces are in general more
poor, it is possible, that there is a higher crime rate because of it.

### Solved Cases vs Suspects

Now that we analyzed the aspects of the solvage rate in Germany, We wanted to have a look at the suspects involved in solving a case. How many suspects
do you need to close a case? Are more suspects better for solving the case? <br/>
One note upfront for this, if a group of people is committing a crime together, every one of them will get their own law suite, which means that every 
crime listed in our data set has only one person that executed it. Also a person will only be listed once per crime, so if person x committed fraud twice
and theft once, then he will appear both in the fraud and theft section only once as a suspect. This means, that a crime with 100% solvage rate and
a lower amount of suspects than detected cases is only explainable by repead offenders. <br/>
For sum keys about the suspects the same rules apply, so a suspect that commits multiple crimes for the same sum key will only be counted once, so 
summing up all capture keys contained in a sum key will often lead to a higher number of suspects than what is written in the sum key.


Note: Points underneath the line are suspected many times
Note: One case -> one person that did it (every one in the case gets its own law suite)
```{r Suspects_Per_Case}
par(mfrow=c(3,1))
filtered <- filter(germanCaptureSet, detected_cases >= solved_cases)
plot(filtered$detected_cases, filtered$suspects, 
     xlim = c(0,8000),
     ylim = c(0,8000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Detected Case",
     xlab = "Detected Cases",
     ylab = "Suspects")
abline(coef = c(0,1))

plot(filtered$solved_cases, filtered$suspects, 
     xlim = c(0,8000),
     ylim = c(0,8000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Solved Cases",
     ylab = "Suspects")
abline(coef = c(0,1))
plot(filtered$solved_cases, filtered$suspects, 
     xlim = c(0,8000),
     ylim = c(0,8000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Solved Cases",
     ylab = "Suspects")
abline(coef = c(0,1))
par(mfrow=c(1,1))
```

```{r}
par(mfrow=c(3,2))
plot(filtered$distribution_under_20K, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (under 20K inhibitants)",
     ylab = "Detected Cases")
abline(coef = c(0,1))
plot(filtered$distribution_20K_to_100K, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (20k - 100K inhibitants)",
     ylab = "Detected Cases")
abline(coef = c(0,1))
plot(filtered$distribution_100K_to_500K, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (100k - 500K inhibitants)",
     ylab = "Detected Cases")
abline(coef = c(0,1))
plot(filtered$distribution_over_500K, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (over 500K inhibitants)",
     ylab = "Detected Cases")
abline(coef = c(0,1))
plot(filtered$distribution_unknown, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (unknown inhibitants)",
     ylab = "Detected Cases")
abline(coef = c(0,1))
plot(filtered$distribution_unknown, filtered$detected_cases, 
     xlim = c(0, 7000),
     ylim = c(0, 7000),
     col = "#cc0000",
     pch = 19,
     main = "Suspects per Solved Case",
     xlab = "Cases in City (unknown inhibitants)",
     ylab = "Detected Cases")
par(mfrow=c(1,1))
```

```{r}
par(mfrow=c(3,2))
plot(germanNonZeroSet$suspects, germanNonZeroSet$male,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Male",
     xlab = "Suspects",
     ylab = "Male Suspects")
abline(coef = c(0,1))
plot(germanNonZeroSet$solved_cases, germanNonZeroSet$male,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Male",
     xlab = "Suspects",
     ylab = "Male Suspects")
abline(coef = c(0,1))
plot(germanNonZeroSet$suspects, germanNonZeroSet$female,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Female",
     xlab = "Suspects",
     ylab = "Female Suspects")
abline(coef = c(0,1))
plot(germanNonZeroSet$suspects, germanNonZeroSet$non_german,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Non German",
     xlab = "Suspects",
     ylab = "Non German Suspects")
abline(coef = c(0,1))
plot(germanNonZeroSet$male, germanNonZeroSet$non_german,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Male",
     xlab = "Suspects",
     ylab = "Male Suspects")
abline(coef = c(0,1))
plot(germanNonZeroSet$suspects, germanNonZeroSet$male,
     xlim=c(0,8000),
     ylim=c(0,8000),
     col="#cc0000",
     pch = 19,
     main = "Suspects vs Male",
     xlab = "Suspects",
     ylab = "Male Suspects")
abline(coef = c(0,1))
par(mfrow=c(1,1))
```

```{r}
reg <- lm(germanNonZeroSet$male~germanNonZeroSet$suspects)
summary(reg)
cor(germanNonZeroSet$suspects, germanNonZeroSet$male)
```




```{r}
par(mfrow=c(2,2))
plot(germanCaptureSet$suspects, germanCaptureSet$male, main = "Something", ylab = "Suspects", xlab = "Male")
plot(germanCaptureSet$suspects, germanCaptureSet$female, main = "Something", ylab = "Suspects", xlab = "Female")
plot(germanCaptureSet$suspects, germanCaptureSet$non_german, main = "Something", ylab = "Suspects", xlab = "Non German")
plot(germanCaptureSet$suspects, germanCaptureSet$solved_cases, xlim=c(0,150000), ylim=c(0,150000), main = "Something", ylab = "Suspects", xlab = "Cases")

par(mfrow=c(1,1))
```

```{r}
filter(merge(germanCaptureSet, crimeOverview, by="key"), suspects/detected_cases >= 0.9 & suspects/detected_cases <= 1.1)
```


```{r}
filter(crimeOverview, key == "731800")
```


```{r}
ggplot(
  data = filter(germanCaptureSet, detected_cases/inhabitants > 0.001),
  mapping = aes(detected_cases/inhabitants, solved_cases/detected_cases)) +
  #geom_point() +
  #geom_smooth(method="lm")
  geom_text(mapping = aes(label = key))
```


## Model 




